Equations & R Code

### 2017-03-13 manuscript/coexistence-stability_ms.Rmd
finished conclusion writing

LIMITATIONS AND CONCLUSIONS
---------------------------
\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship assuming fluctuation-dependent ceoxistence have a three decade head-start, and we have some catching up to do.
In particular, theory has identified numerous context-dependent processes that determine how much diversity can buffer ecosystem variability} [see @Thibaut2013 for a review].
\new{And we ignored several potentially important processes and phenomena to make our current analysis tractable.}

@@

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} @Thibaut2013 \new{show that positive diversity--ecosystem variability relationships are possible.
Specifically, ...}
\new{Likewise, recent advances on quantifying the storage effect in natural communities} [@Ellner2016] \new{opens the door to linking storage effect strength to the capacity of communities to buffer themselves from increasing environmental variability.
Thus, embedding modern coexistence theory within theory on biodiversity and ecosystem functioning likely has broad practical applications.}

>>>>

LIMITATIONS AND CONCLUSIONS
---------------------------
\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship assuming fluctuation-independent ceoxistence have a three decade head-start, and we have some catching up to do.
In particular, theory has identified numerous context-dependent processes that determine how much diversity can buffer ecosystem variability} [see @Thibaut2013 for a review].
\new{And we ignored several potentially important processes and phenomena to make our current analysis tractable.}

@@

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} @Thibaut2013 \new{show that positive diversity--ecosystem variability relationships are possible.
This occurs in their model because total community size, species' abundances, and species' variances are all allowed to systematically vary with species richness.
They use empirical scaling relationships to define how the mean of species and community abundance scale with species richness, but do not attribute a biological mechanism for the relationship.
Though not discussed in detail above, we found that total community abundance increased with species richness under relative nonlinearity because different species had different maximum growth rates in relation to resource availability.
We suspect that many abstract formulations in previous theory can be explained biologically by fluctuation-dependent coexistence.}

\new{Recent advances on quantifying the storage effect in natural communities} [@Ellner2016] \new{opens the door to linking storage effect strength to the capacity of communities to buffer themselves from increasing environmental variability.
The storage effect has special properties beyond species having unique responses to environmental fluctuations, which alone tells us something about how communities might respond to increased variability.
The storage effect also requires that competition positively covary with environmental fluctuations and that populations be buffered in some way to large population declines.
Together, these requirements help species to avoid competitive exlcusion \emph{and} the negative effects of environmental variability (e.g., large declines during a series of bad years).
Knowing the total contribution of the storage effect to coexistence --- not just the dissimilarity of species' responses to the environemnt --- may also inform how communities might respond to increased environmental variability.
Thus, embedding modern coexistence theory within theory on biodiversity and ecosystem functioning likely has broad practical applications.}

### 2017-03-13 manuscript/coexistence-stability_ms.tex
finished conclusion writing

\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship assuming fluctuation-dependent ceoxistence have a three decade head-start, and we have some catching up to do.
In particular, theory has identified numerous context-dependent processes that determine how much diversity can buffer ecosystem variability}
(see Thibaut \& Connolly 2013 for a review).
\new{And we ignored several potentially important processes and phenomena to make our current analysis tractable.}

@@

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} Thibaut \& Connolly (2013)
\new{show that positive diversity--ecosystem variability relationships are possible.
Specifically, ...}
\new{Likewise, recent advances on quantifying the storage effect in natural communities}
(Ellner et al. 2016)
\new{opens the door to linking storage effect strength to the capacity of communities to buffer themselves from increasing environmental variability.
Thus, embedding modern coexistence theory within theory on biodiversity and ecosystem functioning likely has broad practical applications.}

>>>>

\new{What we have presented here is clearly just a beginning.
Theoretical explorations of the diversity--ecosystem variability relationship assuming fluctuation-independent ceoxistence have a three decade head-start, and we have some catching up to do.
In particular, theory has identified numerous context-dependent processes that determine how much diversity can buffer ecosystem variability}
(see Thibaut \& Connolly 2013 for a review).
\new{And we ignored several potentially important processes and phenomena to make our current analysis tractable.}

@@

\new{Perhaps most important will be linking our results from a specific mechanistic model to more general quantitative frameworks.
Using a very general model,} Thibaut \& Connolly (2013)
\new{show that positive diversity--ecosystem variability relationships are possible.
This occurs in their model because total community size, species' abundances, and species' variances are all allowed to systematically vary with species richness.
They use empirical scaling relationships to define how the mean of species and community abundance scale with species richness, but do not attribute a biological mechanism for the relationship.
Though not discussed in detail above, we found that total community abundance increased with species richness under relative nonlinearity because different species had different maximum growth rates in relation to resource availability.
We suspect that many abstract formulations in previous theory can be explained biologically by fluctuation-dependent coexistence.}

\new{Recent advances on quantifying the storage effect in natural communities}
(Ellner et al. 2016)
\new{opens the door to linking storage effect strength to the capacity of communities to buffer themselves from increasing environmental variability.
The storage effect has special properties beyond species having unique responses to environmental fluctuations, which alone tells us something about how communities might respond to increased variability.
The storage effect also requires that competition positively covary with environmental fluctuations and that populations be buffered in some way to large population declines.
Together, these requirements help species to avoid competitive exlcusion \emph{and} the negative effects of environmental variability (e.g., large declines during a series of bad years).
Knowing the total contribution of the storage effect to coexistence --- not just the dissimilarity of species' responses to the environemnt --- may also inform how communities might respond to increased environmental variability.
Thus, embedding modern coexistence theory within theory on biodiversity and ecosystem functioning likely has broad practical applications.}
